---
title: "Red-legged cormorant uses plastic as nest material in an artifical breeding colony of Atacama Desert coast"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

As the amount of plastic debris in both marine and terrestial areas is increasing it imposes dangers to birds by either entanglement or ingestion. Along with this, plastic debris has also been observed in nest as a nesting material among various species of birds. This paper explores the use of various plastics as nest material among red-legged cormorants colonies located in two major seaport areas in Northern Chile. 

## Methods

The researchers collected their data from 18 abandoned nests located along the two seaport areas. 

## Results and Conclusion 


```{r cars}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readxl)
Assignment_5data_ <- read_excel("Assignment_5data .xlsx", 
    col_types = c("text", "numeric"))
View(Assignment_5data_)
view(Assignment_5data_)
ggplot(data = Assignment_5data_, mapping = aes(x = Plastic_type, y = Percentage_of_plastic)) + geom_point() + labs(x = "Type of plastic", y = "Percentage of plastic (%)") + scale_y_continuous(limits = c(0, 50), breaks = c(0, 10, 20, 30, 40, 50), labels = c('0', '10', '20', '30', '40', '50'))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
